An analysis of interrelations between economic and environmental variables in Australian Winegrowing.

### 2023-10-04 article.tex
answered basic questions re intro

% TODO:
% 
% Below is the original comment. BUT you have since come up with more of a scheme that answers these questions (in the bayesian paper). Use this to extrapolate on the introduction.
% 
% You obviously have no leading question for this paper, and although you do a good job at creating accurate models; it is more important that the research is asking a good question. A cool question as Kate puts it.
%
% The questions I put forward to you are:
%
%  How do winegrowing regions differ?
%  Why is a region different?
%  How do regional differences affect winegrowing?
%  What differences are important between winegrowing regions?
%  
%%

% FIXME:
% Whats been done? Whats the persistant gap? Why is a data-driven approach the answer?

>>>>

% TODO:
% %%%%%%%%%%%%%%%
% Paper setup %
%%%%%%%%%%%%%%%

% What is your topic?
Economic sustainability of vineyards.

% What is the context for your reserach?
An unprecedented amount of data regarding the Australian wine and vine industry has been collected through Sustainable Winegrowing Australia offering new insights into the driving economic forces of the Australian wine industry.

% What do you want to achieve?
We hope to uncover the driving relationships and factors of economic sustainability in Australian Winegrowing.

% Are there any relationships you want to explore?
We explore the relationship between various operational and resource use variables to operational costs and vineyard gross margin.

%%%%%%%%%%%%%%%%
% Working title
%

% Description
% NB Avoid titles along the lines of: “Effects of ...”, “The role of ...”, etc.  Be specific about the effect and its significance so that your reader knows what is on offer.
%  TODO:

% For example, rather than write a title like “The effect of factor X on astrophysical properties of green cheese.”,

% be specific about the effect and write something more like ...

% “Factor X halves the lunar thermal diffusivity of  green cheese”.

% You will usually find it easier to write an effective title if you make your title a sentence.

% Notes
% N/a

%%%%%%%%%%%%%%%%%%%%
% Intended readers
%
% Agricultural economists
% Growers
% Property managers (beyond winegrowing)
% Mardi seemed super interseted - I know a lot of growers would be interested, however I am not sure of any names in particular beyond the usual cases such as Hans, David Klassen etc.
% Perhaps those seeking to purchase a property.

% Description:
% Name 4 or 5 potential readers - give their names and why they would be interested  (e.g. “Ichabod Crane, paleo-fudgologist interested in polygalactic fudginomiality”, not “assorted paleo-fudgologists”).

% Your readers should be outside your institution.

%%%%%%%%%%%%%%%%%%%%%
% Anticipated Journal
%
% Wiley Journal of Agricultural Economics
% https://onlinelibrary.wiley.com/journal/14779552

% Descrption
% Ensure that all readers are likely to read the nominated journal  (e.g.  few non-researchers read refereed academic journals; politicians simply don’t read).

% Notes
% Contributors to the JAE should note that, in choosing subjects for articles, the objects of the Society are ‘to promote the study and teaching of agricultural economics and relevant disciplines, and their application to issues in the agricultural, food and related industries, rural communities and the environment. The relevant disciplines include economics, statistics, marketing, business management, politics, history and sociology'. Preference will be given to articles which deal either with new developments in research and methods of analysis, or apply existing methods and techniques to new problems and situations which are likely to be of general interest to the Journal’s international readership. The Journal is not a suitable publication for articles of purely local interest.  Articles should be clearly and concisely written and should normally not exceed 7,000 words. Articles greatly in excess of this limit cannot be considered for publication.

%%%%%%%%%%%%
% Question %
%%%%%%%%%%%%

% Things to consider
%
% Why is the knowledge important?
A better understanding of driving economic factors within agricultural industries helps to drive sustainability through understanding relationships between factors better.
%  FIXME: work on this^

% What is the significance?
This broad dataset has not yet been analysed, showing new insights into the driving factors of the Australian winegrowing industries economy

% How will the findings be utilised?
These findings can be used by growers and property managers to help understand the driving factors that affect their operational costs and gross margins.

% What improvements may be derived from this result?
These insights help to optimise the gross margin and minimise the operational cost of a vineyard.

% Are the terms well defined?
% Some terms need more definition.

% Is it doable? (cost & ethics)
%  ITs done!
%       Can you finish it in time?
% Do experts think your question is important/relevant/doable?
%  Mardi was pretty excited about it!

% What is the nature of your question?
%         who, what, where, when, why, how?
The primary nature of this question is what, and then how: What are the driving factors for operational cost? And, how do these factors relate to each other?

% You can have more than one question.

% What is the most important question your paper will pose?
What are the driving factors for operational cost and gross margin in Australian Winegrowing?

%
% NB It is essential that your answer is framed as a direct question.  Your response must end with a question mark.

% Why is the question/issue/problem worth examining?
There is a lot of economic pressure on Australian winegrowers and the wine and vine industry in general due to international market changes, tighter requirements for organic and sustainability credentials and a shrinking market.
% FIXME: Get some references in here!

% Briefly outline the problem you are tackling and explain why the problem is important to knowledge in general.  “Nothing much is known” is not sufficient justification by itself.  You have to show why the gap in knowledge is important.  Expect to draw heavily on your reading of the literature in framing your answer but do not get into detail of  author and year.

%%%%%%%%%%
% Answer %
%%%%%%%%%%

% What is the answer to question
Region is a driving force in determining profits.
Fuel and water are the primary driving operational costs

%
% 
% NB  You must give a direct answer to the question posed.
% Notes

% Will the findings be considered significant?
The finding themselves are not that significant, it is the evidence of a complex system governing these relationships that is the significant finding.

% How did you gather the evidence? 
%
% Briefly outline the methods you used to gather your evidence.
They were gathered by Sustainable Winegrowing Australia

% What is the main evidence?
%
% Briefly outline the key results.  Focus on outcomes.

% What can you add to theory?
%  
% A research paper has to add to broader understanding. What will yours contribute?  Think about how your results and conclusions will change how people see the world.
What we add is that agricultural economics maybe complex systems that are obfuscated by the expertise of growers to navigate problems such as drought, pests and disease. These systems, although predictable through some variables are not causal. We see this in the evidence of some years not affecting outcomes even though they are known to contain the aforementioned issues. % TODO: use the evidence of draught to be an example. Show why year should be important but is not!

%
% Many people have trouble with this section.   Do not recycle the results.  Focus on the conceptual models that explain why your results are as they are, or why they are different from what might have been expected.  Your contribution may be something new or it may be confirmation of something already known but in a slightly different context.
%
% Sometimes the contribution to theory is not a simple answer but a better understanding of the questions that ought to be asked in future.
%
% Again, expect to draw heavily on the literature in framing your answer, but cite the literature only sparingly here (you can go into full detail when you prepare your discussion).

% What can you add to practice?
%
% Superior research also has practical consequences.  What are the consequences of your work?  Think about how your results and conclusions might change what people do. Do not merely restate your results.
It maybe better to pursue more causal models and create decision support systems than to model factors directly. It is difficult to untangle the predictive and correlative nature of the variable compared to the causal reasons.

%%%%%%%%%%%%%%%
% Future work %
%%%%%%%%%%%%%%%

% What remains unresolved?
% 
% You may or may not have a lot to say here.  Some of it may be useful in your discussion.
The causal reasoning behind these variables behaviours. The untangling the multicollinearity of these variables.
% FIXME:
% Whats been done? Whats the persistant gap? Why is a data-driven approach the answer?
A data driven approach can highlight the significance between different factors. And, highlight how heavily these factors relate through their relative importance.
% Predictive Modeling: When the research goal involves making predictions or forecasts, a data-driven approach, particularly using machine learning algorithms, can analyze historical data to build predictive models. These models can be used to make future predictions or test hypothetical scenarios.
% Exploratory Research: When the research area is relatively unexplored, and there is limited theoretical framework or prior research to build upon, a data-driven approach can help in exploring patterns, trends, and relationships in the available data. This can lead to the formulation of new hypotheses and research directions.
% Large and Complex Datasets: When dealing with large volumes of data that are too complex to be analyzed using traditional methods, data-driven techniques such as machine learning algorithms, data mining, or big data analytics can help in uncovering meaningful insights that might not be apparent through conventional approaches.
